Parallel Test

### 2025-04-16 ParallelTest.Rmd
Cheng's fix and sketch in data poor scenarios

```{r}
sub.dir = "Results"
dir.create(file.path(getwd(), sub.dir), recursive = TRUE)

@@

@@

>>>>

```{r, eval=FALSE}
sub.dir = "Results"
dir.create(file.path(getwd(), sub.dir), recursive = TRUE)

@@

base.years      <- year_start:year_end # Burn-in period
first.year      <- head(base.years,1)
terminal.year   <- tail(base.years,1)
assess.years    <- seq(terminal.year, tail(om$years,1)-assess.interval,by = assess.interval)

@@

That isn't working

Try the low data example that worked individually, first the setup

```{r}
agg_index_sigma = input$data$agg_index_sigma
agg_index_sigma[31:60,] = 0.6 # Increase CV for both survey indices in the feedback period
index_Neff = input$data$index_Neff
index_Neff[31:60,] = 50 # Decrease ESS for both survey indices in the feedback period

#alternate years fall and spring surveys
remove_agg = TRUE # remove a aggregate index for some years
remove_agg_pointer = c(1,2) # both
remove_agg_years = matrix(data=c(seq(31,60,2), seq(32,60,2)), nrow=15, ncol=2) #alternating years by survey
remove_paa = TRUE # Also remove age comp for that index 
remove_paa_pointer = c(1,2) # both
remove_paa_years = matrix(data=c(seq(31,60,2), seq(32,60,2)), nrow=15, ncol=2) #alternating years by survey

input <- update_input_index_info(input, agg_index_sigma, index_Neff,
                                 remove_agg, remove_agg_pointer, remove_agg_years,
                                 remove_paa, remove_paa_pointer, remove_paa_years) # Update input file

agg_catch_sigma = input$data$agg_catch_sigma
agg_catch_sigma[31:60,] = 0.2 #double catch CV in the feedback period
catch_Neff = input$data$catch_Neff
catch_Neff[31:60] = 50

input <- update_input_catch_info(input, agg_catch_sigma, catch_Neff)

om <- fit_wham(input, do.fit = F, do.brps = T, MakeADFun.silent = TRUE)

Now run in parallel, 3 year assessment

```{r}
assess.interval <- 3 #

base.years      <- year_start:year_end # Burn-in period
first.year      <- head(base.years,1)
terminal.year   <- tail(base.years,1)
assess.years    <- seq(terminal.year, tail(om$years,1)-assess.interval,by = assess.interval)

  saveRDS(mod, file.path(sub.dir,sprintf("Mod3_%03d.RDS",i)))

And degraded data with a 6 year assessment

base.years      <- year_start:year_end # Burn-in period
first.year      <- head(base.years,1)
terminal.year   <- tail(base.years,1)
assess.years    <- seq(terminal.year, tail(om$years,1)-assess.interval,by = assess.interval)

  saveRDS(mod, file.path(sub.dir,sprintf("Mod4_%03d.RDS",i)))
